### 2021-11-13 NSF2021/Description/specificaim1.tex
fingers crossed

\subsection{Specific Aim 1: Measuring material properties of amphiphile
  self-assembly}
\label{subsec:specific_aim_1}

The proposed research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.  Specific Aim 1 achieves this
through a novel mathematical model for particle self-organization driven
by long-range interfacial forces.

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[10]{r}{0.55\textwidth}
  \centering
  \vspace{-12pt}
  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
  \caption{\label{fig:flow_map} A collection of amphiphilic particles
  suspended in a solvent. The solvent velocity satisfies the Stokes
  equations, and the hydrophobic forces depend on the solvent activity
  that satisfies the screened Laplace equation. The geometry is updated
  by solving the mobility problem.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of linear
partial differential equations (PDEs) and comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent, which we solve with a
second-order Adams-Bashforth method. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega$ is the fluid region surrounding the
particles. Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$. Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. Experimental measurements suggest that the free energy
functional take the form 
\begin{align*}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align*}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
\cite{MaGa13}. Since waters reorient on a time scale much smaller than
the particle motion, $u$ minimizes $F[u]$ at all time, and therefore
satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle motions (Figure~\ref{fig:bcs}).

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations \eqref{eq:stokes} and the
semilinear elliptic equation \eqref{eq:SL} comes from the first
variation of the energy functional. The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces. It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$
along the particle boundary. The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step.  The particle
boundaries are nearly touching and this requires high-order numerical
schemes to accurately calculate forces and adaptively chose an
appropriate time step size. Furthermore, there are issues with
accurately capturing the far-field boundary conditions in the unbounded
domain. Finally, the numerical routine must handle large system sizes
efficiently when their are many particles is large.

@@

\subsubsection{Janus-particle self-assembly} 
When $f(u) = u^2$, and the water structure has its lowest potential
value at $u=0$ which represents bulk water. The solutions of
\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
bulk with the decay length $\rho$. Even in this linear response case, a
number of morphologies arise by altering boundary conditions.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
    \end{center}
  \caption{\label{fig:self-assemblyA} Self-assembly with a polar
  boundary condition leads to a checkerboard pattern. Green is for $u <
  0$, yellow is for $u > 0$, and blue is for $u = 0$.}
\end{figure}

Consider a polar boundary condition where $g_i(\xx) = (\pi r)^{-1/2}
\cos (\theta_i(\xx))$ where $\theta_i$ is the angle formed by $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$. The
normalization $(\pi r)^{-1/2}$ and others below provide a uniform
surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$ for circular particles
of radius $r$. The boundary condition is odd along the particle axis
making the particle head repel the tail.  We simulate the dynamics of
100 particles with random initial position and orientation. The
particles rapidly form chains with their directors perpendicular to the
length of the chain. The equilibrium structure consists of particles
positioned on a square grid in a checkerboard pattern
(Figure~\ref{fig:self-assemblyA}. This patterning is a consequence of
energy minimality and allows each particle to simultaneously coordinate
its head with the head of three other particles and its tail with the
tail of three other particles.

\begin{figure}[h!]
\begin{center}  
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}
\end{center}    
  \caption{\label{fig:self-assemblyB} Self-assembly with with boundary
  condition that results in hydrophobic tails and hydrophilic heads. The
  resulting bilayer pattern shields the hydrophobic core (yellow) from
  the aqueous phase.}
\end{figure}
Amphiphilic particles have a hydrophobic tail and a hydrophilic head and
are accounted for as follows. The hydrophilic side takes the value $u =
0$ since the apolar head of a lipid, for example, does not alter
the structure of adjacent waters. The hydrophobic side takes the value
$u > 0$. The interaction between particles is attractive. Using $(3\pi
)^{-1/2}(1 + \cos(\theta_i(\xx)))$ as a simple modification to
the previous boundary condition produces two-dimensional micelles and
bilayers \cite{Fu2018_SIAM} (Figure~\ref{fig:self-assemblyB}).
Researchers have asked us if the phenomenon is robust. To show that it
is, we instead use the boundary condition
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}
\end{equation}
where the radicand \todo{radicand?} is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero. The
square of this function behaves as a normal distribution with variance
like $1/\kappa_i$.To replicate experimental conditions, the
concentration $\kappa_i$ and radii $r_i$ are randomized. Using the same
initial configuration, the particles form small groups that
combine to form bilayers (Figure~\ref{fig:self-assemblyC}.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
    \caption{Hydrophobic particles with a bias. The hydrophobic
    intensity is greater on one side of the particle (magenta) than the
    other (yellow).
    \label{fig:self-assemblyC}}
\end{center}
\end{figure}

Multilamelar bilayers arise with an increase by shifting the boundary condition
further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\xx)))$.
This gives a hydrophobic particle with greater intensity of hydrophobicity
at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
is similar to that of the amphiphilic particle case, except that the bilayers
do not stay well separated.  Rather, the bilayers stack on top of each
other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.

In summary, the hydrophibic interaction-mobility problem model yields
rich morphologies that are valuable in the synthesizing multiphasic and
anisotropic colloids \cite{Bradley2016,Mallory2017,Bradley2017}.
The main experimental challenges include the ability to
decouple particle surface properties.
The goal is to obtain numerically aided 
syntheses and assembly of soft matter materials.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-change to amplify colloid
utility for a wide range of  spanning environmental remediation to drug
delivery \cite{McBr21, HaBr20}.

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}
The main modeling challenge is to translate the phenomenological
parameters, e.g. boundary conditions, into measurable quantities
such as contact angles. Collaboration with experimental groups will
use numerical methods to predict parameter regimes 
to control particle-particle interactions. In Specific Aim 3, we
discuss how to include ions and surface charge.

\subsubsection{Hydrophobic forces as capillary wetting}
A natural generalization of the linear response model is to use a
fourth-order, tilted double-well potential $f(u) = a(u-u_0)^2(u-u_1)^2 +
bu$. Motivated by capillary wetting, soft matter physicist Gerhard
Gompper introduced a double-well model for one-dimensional hydrophobic
attraction \cite{GoHaKo94}. The two-dimensional attraction we propose is
more complicated and includes extra line tension effects not present in
the one-dimensional theories.

Here, the order parameter $u$ is the mean number of nearest neighbors
per water molecule. The value $u_0 = 4$ gives a local minimum for the
ideal tetrahadral water network found at hydrophobic surfaces. The value
$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
mixture of four and five-coordinated waters. When particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition.

Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example. PI RR and colaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

One potential application of the Allen-Cahn-type formulation is to
explaning measured hydrophobic attraction profiles.
The experimental data on hydrophobic attraction between 
is well-established and the literature contains data for a number of
solvents and hydrocarbon species. The experimental measurements
are well-fit by a double exponential curve in the 10 to 100 nanometer range
of separation. Below 10~nm, however, there is an amplification of force
and the attraction follows a much steeper force law not accounted
for by past phenomenoloical theories~\cite{Lin2005}.

It may be the case that the double-well formulation recreates the long
and short-range interactions. The advantage is that the two-dimensional
simulations can replicate the experimental setup better than prior,
one-dimensional theoretical work Some of the model parameters directly
connect to long-range decay lengths and energy cost of creating
hydrophobic-water interfaces with established ranges of values. Other
parameters, like the well structure, are fit to the measured data. These
base-line simulations will allow us to move on to provide more accurate
colloidal suspension simulations.

Other approaches will be required if the modified phenomenological
theory does not recreate the measured force curves. We can rule out
convection in the water structure since the time scale of particle
motion is much larger than the hydrogen-bond lifetimes. One approach is
to consider Gaussian fluctuation. Here, we expand the free energy
functional around the saddle point solution. The fluctuation energy
then involves calculation of the eigenfunctions of the second variation
of the free energy. This accounts for the fact that experimental
measurements are carried out at finite temperatures, where thermal
fluctuations should ideally also be considered.

>>>>

\subsection{Specific Aim 1: Measuring material properties of amphiphile
  self-assembly}
\label{subsec:specific_aim_1}
Specific Aim 1 proposes a novel mathematical model for particle
self-organization driven by long-range interfacial forces. 
The research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]
\begin{wrapfigure}[11]{r}{0.55\textwidth}
 \centering
 \vspace{-3pt}
 \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
 \caption{\label{fig:flow_map}
   In the HAP formulation, hydronamic interactions
   come from the Stokes equations and
   hydrophobic interactions come from the structure order parameter $u$.}
\end{wrapfigure}

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent, which we solve with a
second-order Adams-Bashforth method. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional take the form 
\begin{align*}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align*}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

The density~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions.

@@

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently when the number of particles is large.

@@

\subsubsection{Janus-particle self-assembly} 
Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(a)} & \text{(b)} & \text{(c)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
The normalizations, e.g. $(\pi r)^{-1/2}$, provide a uniform
surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
of radius $r$. 
The cases (b) and (c) are obtained by applying a vertical shift
and scaling to case (a), which amounts to changing one line of code. 
Using this setup, we simulate the dynamics of 100 particles with random
initial position and orientation.

Case (a) models amphiphilic particles.
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and these are accounted for as follows.
The hydrophilic side takes the value $u =0$.
This mimicks the apolar head of a lipid, for example, which does
not alter the structure of adjacent waters. The hydrophobic side
represents hydrocarbons and takes the value 
$u > 0$. The interaction between particles is attractive,
and particles will collectively orient their tails toward
one another. 
PIs RR and YNY's previous work showed that this   
boundary condition produces two-dimensional micelles and
bilayers~\cite{Fu2018_SIAM}, as illustrated in 
Figure~\ref{fig:self-assembly}(a).

\begin{wrapfigure}[11]{r}{0.65\textwidth}
  \vspace{-10pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
  \caption{\label{fig:bcs} Boundary conditions characterize the water
    structure at the particle interface: an amphiphilic particle (left),
    a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow is its director.}
\end{wrapfigure}

Multilamelar bilayers arise when both sides of the particle
are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
The boundary condition \eqref{eq:bcs}(b) 
gives a particle with a hydrophobic intensity three times as great
on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
The initial self-assembly is similar to that in case (a).
The difference arises in the long-time dynamics where the bilayers
no longer remain well-separated. 
Rather, the bilayers form layers 
as a consequence of the interfacial tension of exposed particle
heads~\cite{Huetal19, deMeetal21}.

\begin{figure}[h!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
      (a)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.pdf}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.pdf}
     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.pdf}    \\
     (b)
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.pdf}
    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.pdf}    \\
    (c)
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.pdf}
      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.pdf}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
  \end{tabular}
    \end{center}
  \caption{\label{fig:self-assembly}
    Using the same initial configuration,
    particles self-assemble into distinct morphologies based
    on the boundart condition $g.$ 
    boundary condition leads to a checkerboard pattern.
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.
  }
\end{figure}

\todo[inline]{Rationalize and citations for following} 
Finally, boundary condition \eqref{eq:bcs}(c) models 
a particle with oppositelly charged ends making the 
particle heads repel the tails \cite{MaRa76, Ma77}.
The particles initially form chains with their directors perpendicular to the
length of the chain. The equilibrium structure consists of particles
positioned on a square grid in a checkerboard pattern
Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
energy minimality and allows each particle to simultaneously coordinate
its head with the head of three other particles and its tail with the
tail of three other particles.

The ultimate goal is to use numerical simulations to aid
the syntheses soft matter materials.
Applications in this area include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-change to amplify colloid
utility for a wide range of  spanning environmental remediation to drug
delivery \cite{McBr21, HaBr20}.
Here, mathematical models like the kind we propose are crucial
because the model parameters control particle surface properties independently, 
whereas these properties are often difficult to decouple in experiment
~\cite{Bradley2016,Mallory2017,Bradley2017}.

One challenge is translating phenomenological parameters
into measurable quantities.  For example, Janus particles
with uniform surface properties are costly or difficult to
manufacture.  Thus, we can replace the ideal boundary
conditions \eqref{eq:bcs} with a more realistic one like
\begin{equation}
\label{eq:vonMises}
  g_i(\xx) = \sqrt{
  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}.
\end{equation}
Here, the term under the square root is the von Mises distribution with
director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
The square of this function behaves as a normal distribution with variance
like $1/\kappa_i$. We can replicated surface imperfections
by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
for example. Collaboration with experimental groups will
use numerical methods to predict parameter regimes 
to control particle-particle interactions.
In Specific Aim 3, we discuss how to include ions and surface charge.

%\begin{wrapfigure}[14]{l}{0.5\textwidth}
%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
%\caption{\label{fig:multilamelar}
%  Experimentalists can transform unilamellar vesicles to% multilamellar
%  vesicles by altering the quality of the solvent
%    \cite{deMeetal21}.
%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
%  $f(u)$ and boundary conditions. 
%}
%\end{wrapfigure}

\subsubsection{Hydrophobic forces as capillary wetting}
A natural generalization of the linear response potential $f(u) = u^2$
is a fourth-order, tilted double-well potential
$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
Here, the order parameter $u$ is related to
the mean number of nearest neighbors
per water molecule \cite{GoHaKo94}.
The value $u_0$ gives the absolute minimum in the bulk
and $u_1$ gives a local minimum for the
tetrahadral water network found at hydrophobic surfaces.
Figure \ref{fig:CA}(a) illustrates a double-well potential
and Specific Aim 2 describes the numerical implementation issues.

\begin{wrapfigure}[28]{l}{1.8in}
  \vspace{-4pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} (a) The double well potential $u_0 =
  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
  and inexact Newton's methods.}
\end{wrapfigure}
Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
equation. The Allen-Cahn equation is used in phase field formulations of
immisible fluids, for example.
PI BQ has developed fast integral equation solvers for
the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
PI RR and colaborators launched the
simulation and asymptotic analysis of phase field functionals of
membrane elastic energy, devising functionals for for the squared mean
curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
well as energetic variational approaches to coupling membrane elasticity
to fluids~\cite{QiangDu09}.

The key innovation is that when particles are
well-separated, the energetic cost for filling the interstitial region
with $u_0$-phase water is prohibitive and there is a phase shift from
the $u_0$ to $u_1$ water order---the attraction landscape is more or
less identical to the linear response theory. Conversely, when particles
are proximal, it becomes energetically favorable to coalesce
$u_0$-phases. This introduces a line tension for the phase transition
which is an effect not present in the one-dimensional model.

The double-well formulation can potentially 
explain hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
Motivated by capillary wetting, Gerhard
Gompper introduced the double-well model for one-dimensional hydrophobic
attraction \cite{GoHaKo94}.
The results improved on previous work~\cite{ErLjCl89,MaRa76},
but the realistic hydrophobic effect is more
complicated and may involve higher-dimensional geometric features. 
Some of the model parameters directly
%connect to long-range decay lengths and energy cost of creating
%hydrophobic-water interfaces with established ranges of
to well-established experimental values. Other
parameters, like the details of the well structure,
are less well-understood and must be fit to the measured data.
This improved model will allow us to more accurately 
simulate colloidal suspensions.
%The experimental data on hydrophobic attraction between 
%is well-established and the literature contains data for a number of
%solvents and hydrocarbon species.
%The experimental measurements
%are well-fit by a double exponential curve in the 10 to 100 nanometer range
%of separation. Below 10~nm, however, there is an amplification of force
%and the attraction follows a much steeper force law not accounted
%for by past phenomenoloical theories~\cite{Lin2005}.

%It may be the case that the double-well formulation recreates the long
%and short-range interactions. The advantage is that the two-dimensional
%simulations can replicate the experimental setup better than prior,
%one-dimensional theoretical work

\todo[inline]{Below needs citation and more solid explanation}
Other approaches will be required if the modified phenomenological
theory does not recreate the measured force curves.
One such approach is to consider Gaussian fluctuation. Here, we expand
the free energy
functional around the saddle point solution. The fluctuation energy
then involves calculation of the eigenfunctions of the second variation
of the free energy. This accounts for the fact that experimental
measurements are carried out at finite temperatures, where thermal
fluctuations should ideally also be considered.
